### 2025-03-13 paper/sections/other/grids.qmd
final table done

## Grid Searches {#sec-app-grid}

@@

### Evaluation Details

@@

#### Predictive Performance

@@

#### Counterfactual Outcomes {#sec-app-grid-hl}

Overall, we find that Counterfactual Training (CT) achieves it key objectives consistently across all hyperparameter settings and also broadly across datasets: plausibility is improved by up to ~60 percentage points (ppts) for the *Circles* data (e.g. @fig-grid-gen_params-plaus-circles), ~25-30ppts for the *Moons* data (e.g. @fig-grid-gen_params-plaus-moons) and ~10-20ppts for the *Linearly Separable* data (e.g. @fig-grid-gen_params-plaus-lin_sep). At the same time, the average costs of faithful counterfactuals are reduced in many cases by around ~20-25ppts for  *Circles* (e.g. @fig-grid-gen_params-cost-circles) and up to ~50ppts for *Moons* (e.g. @fig-grid-gen_params-cost-moons). For the *Linearly Separable* data, costs are generally increased although typically by less than 10ppts (e.g. @fig-grid-gen_params-cost-lin_sep), which reflects a common tradeoff between costs and plausibility [@altmeyer2024faithful].

@@

### Generator Parameters {#sec-app-grid-gen}

@@

#### Accuracy

@@

@@

#### Plausibility

@@

#### Cost

@@

### Penalty Strengths {#sec-app-grid-pen}

@@

### Other Parameters {#sec-app-grid-train}

>>>>

# Grid Searches {#sec-app-grid}

@@

## Evaluation Details

@@

### Predictive Performance

@@

### Counterfactual Outcomes {#sec-app-grid-hl}

Overall, we find that Counterfactual Training (CT) achieves it key objectives consistently across all hyperparameter settings and also broadly across datasets: plausibility is improved by up to ~60 percent (%) for the *Circles* data (e.g. @fig-grid-gen_params-plaus-circles), ~25-30% for the *Moons* data (e.g. @fig-grid-gen_params-plaus-moons) and ~10-20% for the *Linearly Separable* data (e.g. @fig-grid-gen_params-plaus-lin_sep). At the same time, the average costs of faithful counterfactuals are reduced in many cases by around ~20-25% for  *Circles* (e.g. @fig-grid-gen_params-cost-circles) and up to ~50% for *Moons* (e.g. @fig-grid-gen_params-cost-moons). For the *Linearly Separable* data, costs are generally increased although typically by less than 10% (e.g. @fig-grid-gen_params-cost-lin_sep), which reflects a common tradeoff between costs and plausibility [@altmeyer2024faithful].

@@

## Generator Parameters {#sec-app-grid-gen}

@@

### Accuracy

@@

df = CTExperiments.aggregate_performance(eval_grids; byvars=["objective"]) 
get_table_inputs(df, "mean";backend=Val(:latex)) |>
    inputs -> tabulate_results(inputs; wrap_table=false)
```

@@

### Plausibility

@@

### Cost

@@

## Penalty Strengths {#sec-app-grid-pen}

@@

## Other Parameters {#sec-app-grid-train}

### 2025-03-13 paper/sections/other/tuning.qmd
final table done

## Hyperparameter Tuning {#sec-app-tune}

@@

Finally, to increase the proportion of mature counterfactuals for some datasets, we have also investigated the effect on the learning rate $\eta$ for the counterfactual search and even smaller regularization strengths for a fixed decision threshold of 0.5 (@fig-tune_lr-plaus-adult to @fig-tune_lr-plaus-over). For the given low decision threshold, we find that the learning rate has no discernable impact on the proportion of mature counterfactuals (@fig-tune_lr-mat-adult to @fig-tune_lr-mat-over). We do notice, however, that the results for MNIST are much improved when using a low value $\lambda_{\text{reg}}$, the strength for the engery regularization: plausibility is increased by up to ~10ppt (@fig-tune_lr-plaus-mnist) and the proportion of mature counterfactuals reaches 100%.

@@

### Key Parameters {#sec-app-tune-key}

@@

#### Proportion of Mature CE

@@

### Learning Rate {#sec-app-tune-lr}

>>>>

# Tuning Key Parameters {#sec-app-tune}

@@

Finally, to increase the proportion of mature counterfactuals for some datasets, we have also investigated the effect on the learning rate $\eta$ for the counterfactual search and even smaller regularization strengths for a fixed decision threshold of 0.5 (@fig-tune_lr-plaus-adult to @fig-tune_lr-plaus-over). For the given low decision threshold, we find that the learning rate has no discernable impact on the proportion of mature counterfactuals (@fig-tune_lr-mat-adult to @fig-tune_lr-mat-over). We do notice, however, that the results for MNIST are much improved when using a low value $\lambda_{\text{reg}}$, the strength for the engery regularization: plausibility is increased by up to ~10% (@fig-tune_lr-plaus-mnist) and the proportion of mature counterfactuals reaches 100%.

@@

## Key Parameters {#sec-app-tune-key}

@@

### Proportion of Mature CE

@@

## Learning Rate {#sec-app-tune-lr}
